Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-17 cordillera-cycle.tex
Highlight headers in LaTeX source.
Add new outline.

% cordillera-climate.tex
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\begin{document}
\linenumbers
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\introduction
\label{sec:intro}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\section{Model setup}
\label{sec:model}
% ----------------------------------------------------------------------

%\subsection{Forcings}

@@

\noindent\todo{Do we need a new 2.1 subsection title here?}

@@

\subsection{Ice thermodynamics}
\label{sec:icedyn}

@@

\subsection{Surface mass balance}

@@

\subsection{Atmospheric forcing}
\label{sec:atm}

@@

% ----------------------------------------------------------------------
\section{Sensitivity to atmospheric forcing time-series}
\label{sec:results}
% ----------------------------------------------------------------------

@@

@@

% ----------------------------------------------------------------------
\section[Comparison to the geologic record]
        {Comparison to the geologic record\renote{
    Arjen, you have proposed 2.1 Evaluation of model runs agains field
    evidence, 2.2 Palaeoglaciology of the Cordilleran ice sheet, and 2.3 The
    last deglaciation; but I don't think these headers work. In my vision of
    the paper, this entire ``discussion'' part is all about evaluation of model
    runs agains field evidence and palaeoglaciology. Because of this, and
    because we also present new ``results'', or rather different views of the
    same results, I propose to rename it to a more explicit ``Comparison to the
    geologic record'' (or similar). I have also renamed the ``results'' to
    ``Sensitivity to atmospheric forcing time-series'', which is actually what
    that section is about: raw model output, no discussion against the geologic
    record.}}
\label{sec:discussion}
% ----------------------------------------------------------------------

\subsection{Timing of glaciation}

@@

\subsection{Location and longevity of the major ice-despersal centres}

\todo{Add general statements on the scale of glaciation (but where?).}

@@

\todo{Include two paragraphs from Martin, but not here. Make sure that figures
      come in the right order in these paragraphs}.

@@

@@

\subsection{Pace and patterns of deglaciation}

@@

@@

@@

% ----------------------------------------------------------------------
\conclusions
\label{sec:concl}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
% Floats
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\end{document}
\endinput
% ----------------------------------------------------------------------

>>>>

% cordillera-climate.tex
% =============================================================================

@@

% =============================================================================
\begin{document}
\linenumbers
% =============================================================================

@@

% =============================================================================
\introduction
\label{sec:intro}
% =============================================================================

@@

% =============================================================================
\section{Model setup}
\label{sec:model}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{Overview}
% -----------------------------------------------------------------------------

@@

@@

% -----------------------------------------------------------------------------
\subsection{Ice thermodynamics}
\label{sec:icedyn}
% -----------------------------------------------------------------------------

@@

% -----------------------------------------------------------------------------
\subsection{Surface mass balance}
% -----------------------------------------------------------------------------

@@

% -----------------------------------------------------------------------------
\subsection{Atmospheric forcing}
\label{sec:atm}
% -----------------------------------------------------------------------------

@@

% =============================================================================
\section{Sensitivity to atmospheric forcing time-series}
\label{sec:results}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{Evolution of ice volume}
% -----------------------------------------------------------------------------

@@

% -----------------------------------------------------------------------------
\subsection{Extreme configurations}
% -----------------------------------------------------------------------------

@@

\todo{Add general statements on the scale of glaciation.}

% =============================================================================
\section[Comparison to the geologic record]
        {Comparison to the geologic record\renote{
    Arjen, you have proposed 2.1 Evaluation of model runs agains field
    evidence, 2.2 Palaeoglaciology of the Cordilleran ice sheet, and 2.3 The
    last deglaciation; but I don't think these headers work. In my vision of
    the paper, this entire ``discussion'' part is all about evaluation of model
    runs agains field evidence and palaeoglaciology. Because of this, and
    because we also present new ``results'', or rather different views of the
    same results, I propose to rename it to a more explicit ``Comparison to the
    geologic record'' (or similar). I have also renamed the ``results'' to
    ``Sensitivity to atmospheric forcing time-series'', which is actually what
    that section is about: raw model output, no discussion against the geologic
    record.}}
\label{sec:discussion}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{Glacial maxima}
% -----------------------------------------------------------------------------

\subsubsection{Timing of glaciation}

@@

\subsubsection{Ice configuration during MIS~2}

\todo{Add MIS~2 ice topo and velocity map. Include two paragraphs from Martin.}

\subsubsection{Ice configuration during MIS~4}

\todo{Add MIS~4 ice topo and velocity map. Discuss that some of the margins
      are more extensive during MIS~4 than during MIS~2, in the GRIP simu.}

% -----------------------------------------------------------------------------
\subsection{Nucleation centres}
% -----------------------------------------------------------------------------

\subsubsection{Transient ice sheet states}

@@

\subsubsection{Major ice-dispersal centres}

@@

\subsubsection{Potential imprint on the landscape}

@@

% -----------------------------------------------------------------------------
\subsection{The last deglaciation}
% -----------------------------------------------------------------------------

\subsubsection{Pace and patterns of deglaciation}

@@

\subsubsection{Possibility for a late-glacial readvance}

@@

\subsubsection{Deglacial flow directions}

@@

% =============================================================================
\conclusions
\label{sec:concl}
% =============================================================================

@@

% =============================================================================
% Floats
% =============================================================================

@@

% =============================================================================
\end{document}
\endinput
% =============================================================================
